The Astropy Project: \\ Sustaining and Growing a Community-oriented Open-source Project and the Latest Major Release (v5.0) of the Core Package

### 2022-04-05 src/ms.tex
Escape another space
Hyphenate "well-defined" when a compound adjective

\paragraph{Masked quantities}  It can be useful to mask bad data, either by marking
bad data values with a flag or by replacing them with a special
value, e.g., ``Not a Number'' (NaN). In \astropypkg, both approaches are
used: a flag for masked columns in \astropyTable, mask flags and bitmaps
for N-dimensional data in \astropysubpkg{nddata}, and replacing elements with
NaN in \astropyTime. However, masked \astropyQuantity\ support is currently very limited,
hindering usage of masks in a \astropyQTable\ (in which \astropyQuantity\ is used
for all columns with units).

>>>>

\paragraph{Masked quantities}  It can be useful to mask bad data, either by marking
bad data values with a flag or by replacing them with a special
value, e.g., ``Not a Number'' (NaN). In \astropypkg, both approaches are
used: a flag for masked columns in \astropyTable, mask flags and bitmaps
for N-dimensional data in \astropysubpkg{nddata}, and replacing elements with
NaN in \astropyTime. However masked \astropyQuantity support is currently very limited,
hindering usage of masks in a \astropyQTable\ (in which \astropyQuantity\ is used
for all columns with units).
